Online {\IterComp}\\Guided by Low Overhead Profiling

### 2017-09-06 abstract.tex
updates intro

In this thesis, we focus on enabling {\itercomp} in \textit{online} scenarios.
Because of the restriction on repeating the execution with same input, it is
not always feasible to measure the real speedup when comparing optimisations.
To this end, we propose a \textit{work efficiency} metric to guide
online {\itercomp}, which is able to achieve about 80\% of the performance
of the offline oracle, with improvements of up to about 20\%.

>>>>

In this thesis, we focus on enabling {\itercomp} in \textit{online} scenarios.
Because of the restriction on repeating the execution with same input, it is
not always feasible to measure the real speedup when comparing optimisations.
To this end, we propose a \textit{work efficiency} metric to guide
online {\itercomp}, which is able to achieve about 80\% of the performance
of an offline oracle, with improvements of up to 20\%.
